new_analses

### 2021-07-14 new_analyses.Rmd
hjgh

```{r}
biom %>%
  unite("crop_yr", c("crop", "year"), sep = "-") %>% 
  filter(!is.na(weight)) %>% 
  group_by(month) %>% 
  nest(-month) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ crop_yr + 
                                 (1|location), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ crop_yr, 
                                        type = "response"))) -> analysis2
```

@@

```{r}
analysis2$emmeans[[2]] %>% 
  as_tibble() %>% 
  mutate(month = "Second transplanting") -> second2

analysis2$emmeans[[1]] %>% 
  as_tibble() %>% 
  mutate(month = "First transplanting") %>% 
  bind_rows(second2) -> result2
```

>>>>

```{r}
biom %>%
#  unite("crop_yr", c("crop", "year"), sep = "-") %>% 
  filter(!is.na(weight)) %>% 
  group_by(year) %>% 
  nest(-year) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ location * crop * month + 
                                 (1|location), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ location * crop * month, 
                                        type = "response"))) -> analysis2
```

@@

```{r}
analysis2$emmeans[[2]] %>% 
  as_tibble() %>% 
  mutate(year = "2019") -> second2

analysis2$emmeans[[1]] %>% 
  as_tibble() %>% 
  mutate(year = "2018") %>% 
  bind_rows(second2) -> result2
```
